DRAFT: Direct-style process creation on Linux

### 2020-05-15 research/paper/paper.tex
paper

This paper is organized in several sections.
In section \ref{background}, we provide background on fork-style, spawn-style, and direct-style process creation,
and consider their advantages and disadvantages in more depth.
In section \ref{overview} we discuss the design of the API,
including our usage of \texttt{rsyscall}.
In section \ref{applications} we show examples of usage of direct-style process creation in Python on Linux,
including use of process features which are difficult to use on Linux with \texttt{fork} or \texttt{posix\_spawn}.
In section \ref{implementation}, we explore our implementation in depth,
and discuss several difficult process-creation related details of \texttt{rsyscall}'s implementation.
In section \ref{evaluation}, we evaluate, somehow (TODO).
In section \ref{related_work},
we examine other work which also touches on the topics covered by this paper.
In section \ref{future_work},
we list several directions for future work related to direct-style process creation and to \texttt{rsyscall}.
In section \ref{conclusions}, we briefly and optimistically conclude.

@@

By removing the filesystem tree from the view of this process,
we can run this executable with greater confidence
that it won't be able to tamper with the rest of the system.
A sandbox which is truly robust against malicious or compromised programs requires some additional steps,
but this is a substantial start.
Such a technique can also be used when a full sandbox is not relevant,
to ease reasoning about the behavior of the program being run,
and protect against bugs.

@@

\texttt{init} in a pid namespace has some special powers and responsibilities.
We can handle these responsibilities ourselves, directly from this program,
or we can continue on by execing an init daemon in \texttt{init} to handle it for us.

>>>>

This paper is organized in several sections.
In section \ref{background}, we provide background on fork-style, spawn-style, and direct-style process creation,
and consider their advantages and disadvantages in more depth.
In section \ref{overview}, we discuss the design of the API,
including our usage of \texttt{rsyscall}.
In section \ref{applications}, we show examples of usage of direct-style process creation in Python on Linux,
including use of process features which are difficult to use on Linux with \texttt{fork} or \texttt{posix\_spawn}.
In section \ref{implementation}, we explore our implementation in depth,
and discuss several difficult process-creation related details of \texttt{rsyscall}'s implementation.
In section \ref{evaluation}, we evaluate, somehow (TODO).
In section \ref{related_work},
we examine other work which also touches on the topics covered by this paper.
In section \ref{future_work},
we list several directions for future work related to direct-style process creation and to \texttt{rsyscall}.
In section \ref{conclusions}, we briefly and optimistically conclude.

@@

By removing the filesystem tree from the view of this process,
we can run this executable with greater confidence
that it won't be able to tamper with the rest of the system.
A sandbox which is truly robust against malicious or compromised programs requires some additional steps,
but this is a substantial start.
Such a technique can also be used when a full sandbox is not relevant,
to ease reasoning about the behavior of the program being run
and protect against bugs.

@@

\texttt{init} in a pid namespace has some special powers and responsibilities.
We can handle these responsibilities ourselves directly from our program,
or we can continue on by execing an init daemon in \texttt{init} to handle it for us.
